Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-21 Arxiv/main.tex
update plots onprivacy loss

\subsection{Baseline Approaches}
\label{subsec_baselines}

@@

\subsubsection{Improved Baseline Approach}

@@

\subsection{Our approach: smoothed Hellinger distance based exponential mechanism}
\label{subsec_hexpmech}

@@

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved baseline Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-Multinomial system (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[H]
\centering
\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.21\textwidth]{global_epsilon_20_20(2).eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure*}

>>>>

\subsection{Baseline Mechanisms}
\label{subsec_baselines}

@@

\subsubsection{Improved Baseline Mechanism}

@@

\subsection{Our Mechanism: Smoothed Hellinger Distance Based Exponential Mechanism $\hexpmech$}
\label{subsec_hexpmech}

@@

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-Multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
\begin{figure}[H]
\centering
\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure*}
